LAGOS lake depth

### 2020-04-29 tables/01_predictors.Rmd
rm continental comparison for nearshore slope

# remove sample size reporting for bathy specific variables
dt[
  dt$variable %in% c("dist_deepest", "dist_viscenter", "inlake_slope"), 2:5] <- 
  dt[
  dt$variable %in% c("dist_deepest", "dist_viscenter", "inlake_slope"), 2:5] %>%
apply(2, function(x) stringr::str_replace(x, "\\(([^\\)]+)\\)", "(-)"))

>>>>

# remove sample size reporting for bathy specific variables
dt[
  dt$variable %in% c("dist_deepest", "dist_viscenter", 
                     "inlake_slope", "buffer_slope"), 2:5] <- 
  dt[
  dt$variable %in% c("dist_deepest", "dist_viscenter", 
                     "inlake_slope", "buffer_slope"), 2:5] %>%
apply(2, function(x) stringr::str_replace(x, "\\(([^\\)]+)\\)", "(-)"))
